Supporting Information: Improving cropland maps through tight integration of human and machine intelligence

### 2021-01-04 inst/manuscript/manuscript.Rmd
Updates to manuscript, si, added various ignores. New data-raw script for combining label_risk with accuracy metrics.

A second measure of the impact of training data error can be obtained by comparing the average label risk per AOI against the model performance metrics....

>>>>

A second measure of the impact of training data error can be obtained by calculating the Spearman Rank Correlation coefficient between the average label risk per AOI versus various model performance metrics.

### 2021-01-04 inst/manuscript/si.Rmd
Updates to manuscript, si, added various ignores. New data-raw script for combining label_risk with accuracy metrics.

```{r labelrisk_v_metrics, echo=FALSE}
data("label_risk")
data("iteration_metrics")

risk <- label_risk$stats %>% 
  filter(usage == "Train") %>% 
  filter(aoi %in% 1:16) %>% 
  select(-usage)

mets <- c("Accuracy", "AUC", "F1", "TSS", "Precision", "Recall", "FPR")
metrics <- iteration_metrics %>% 
  filter(Metric %in% mets) %>% 
  mutate(AOI = as.factor(gsub("labeller", "", AOI))) %>% 
  filter(AOI %in% 1:16) %>% 
  # pivot_wider(names_from = Metric, values_from = Score) %>% 
  group_by(AOI) %>% filter(Iteration == max(Iteration)) %>% 
  select(-Iteration)

risk_metrics <- left_join(risk, metrics, by = c("aoi" = "AOI"))

@@

cap <- glue::glue("Spearman's Rank correlation between the average label risk per AOI and a variety of model performance metrics.")
kable(risk_corr, format = "latex", booktabs = "T", caption = cap) %>% 
  kable_styling(full_width = TRUE, latex_options = c("hold_position")) #%>% 
  # column_spec(1, width = "8cm")
```

>>>>

```{r labelrisk_v_metrics, echo=FALSE}

@@

cap <- glue::glue("Spearman's Rank correlation between the average label risk per AOI and a variety of model performance metrics.")
kable(risk_corr, format = "latex", booktabs = "T", caption = cap) %>% 
  kable_styling(full_width = TRUE, latex_options = c("hold_position")) #%>% 
  # column_spec(1, width = "8cm")

# tp <- 10
# fp <- 2
# tn <- 20
# fn <- 3
# tss <- (tp * tn - fp * fn) / ((tp + fn) * (fp + tn))
# mcc <- (tp * tn - fp * fn) / sqrt((tp + fp) * (tp + fn) * (tn + fp) * (tn + fn))
